Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-09-03 papers/pair-correlation/paper.tex
nicer formatting in pair paper Tested everything on bingley.

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{align}
  1 + n\int\left[g(r)-1\right]d\rr &= nkT\chi_T
\end{align}
\begin{equation}
  \begin{split}
    \chi_T  &= -\frac{1}{V}\left(\frac{\partial V}{\partial p}\right)_T
    = - \left(V\left(\frac{\partial p}{\partial V}\right)_T\right)^{-1}\\
    p &= nkT\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\\
    \left(\frac{\partial p}{\partial V}\right)_T &= \frac{\partial p}{\partial\eta}\frac{\partial\eta}{\partial V} + \frac{\partial p}{\partial n}\frac{\partial n}{\partial V}\\
    n &= \frac{N}{V}\Longrightarrow \frac{\partial n}{\partial V} = -\frac{N}{V^2} = -\frac{n}{V}\\
    \eta &= \frac{4\pi R^3N}{3V}\Longrightarrow \frac{d\eta}{dV} = -\frac{\eta}{V}\\
    \left(\frac{\partial p}{\partial V}\right)_T &= -nkT\frac{\eta}{V}\left[\frac{1 + 2\eta - 3\eta^2}{(1-\eta)^3} + 3\frac{1 + \eta + \eta^2 - \eta^3}{(1-\eta)^4}\right]\\
    &  - \frac{nkT}{V}\left[\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\right]\\
    &= -nkT\frac{\eta}{V}\left[\frac{(1+2\eta-3\eta^2)(1-\eta) + 3 + 3\eta + 3\eta^2 - 3\eta^3}{(1-\eta)^4}\right]\\
    &  - \frac{nkT}{V}\left[\frac{(1+\eta+\eta^2-\eta^3)(1-\eta)}{(1-\eta)^4}\right]\\
    &= -\frac{kT}{V}\left[\frac{4\eta + 4\eta^2 - 2\eta^3}{(1-\eta)^4} + \frac{1 - 2\eta^3 + \eta^4}{(1-\eta)^4}\right]\\
    nkT\chi_T &= \frac{(1-\eta)^4}{1 + 4\eta + 4\eta^2 - 4\eta^3 + \eta^4}
  %\int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  %&= \eta \eta \cdots \fixme{fill in, double-check}
  \end{split}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.

>>>>

We construct $g(r, g_\sigma)$ using several constraints.  Naturally,
\begin{equation}
  g(\sigma, g_\sigma) = g_\sigma.
\end{equation}
In addition, we know that
\begin{align}
  1 + n\int\left[g(r)-1\right]d\rr &= nkT\chi_T
\end{align}
\begin{equation}
  \begin{split}
    \chi_T  &= -\frac{1}{V}\left(\frac{\partial V}{\partial
      p}\right)_T \\
    &= - \left(V\left(\frac{\partial p}{\partial
      V}\right)_T\right)^{-1}
  \end{split}
\end{equation}
\begin{equation}
    p = nkT\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}
\end{equation}
\begin{equation}
    \left(\frac{\partial p}{\partial V}\right)_T = \frac{\partial p}{\partial\eta}\frac{\partial\eta}{\partial V} + \frac{\partial p}{\partial n}\frac{\partial n}{\partial V}
\end{equation}
\begin{equation}
    n = \frac{N}{V}\Longrightarrow \frac{\partial n}{\partial V} = -\frac{N}{V^2} = -\frac{n}{V}
\end{equation}
\begin{equation}
    \eta = \frac{4\pi R^3N}{3V}\Longrightarrow \frac{d\eta}{dV} = -\frac{\eta}{V}
\end{equation}
\begin{equation}
  \begin{split}
    \left(\frac{\partial p}{\partial V}\right)_T &= -nkT\frac{\eta}{V}\left[\frac{1 + 2\eta - 3\eta^2}{(1-\eta)^3} + 3\frac{1 + \eta + \eta^2 - \eta^3}{(1-\eta)^4}\right]\\
    &\quad  - \frac{nkT}{V}\left[\frac{1+\eta+\eta^2-\eta^3}{(1-\eta)^3}\right]\\
    &= -nkT\frac{\eta}{V}\left[\frac{(1+2\eta-3\eta^2)(1-\eta) + 3 + 3\eta + 3\eta^2 - 3\eta^3}{(1-\eta)^4}\right]\\
    &\quad  - \frac{nkT}{V}\left[\frac{(1+\eta+\eta^2-\eta^3)(1-\eta)}{(1-\eta)^4}\right]\\
    &= -\frac{nkT}{V}\left[\frac{4\eta + 4\eta^2 - 2\eta^3}{(1-\eta)^4} + \frac{1 - 2\eta^3 + \eta^4}{(1-\eta)^4}\right]\\
  \end{split}
\end{equation}
\begin{equation}
    nkT\chi_T = \frac{(1-\eta)^4}{1 + 4\eta + 4\eta^2 - 4\eta^3 + \eta^4}
  %\int (g(r)-1)d\rr &= \frac{\chi_T}{kT} \\
  %&= \eta \eta \cdots \fixme{fill in, double-check}
\end{equation}
where $\chi_T$ is the isothermal compressibility, for which we use the
Carnahan-Starling equation of state.
